\documentclass[addpoints]{exam}
\usepackage{url}
\usepackage{amsmath,amsthm,enumitem}
\usepackage{graphicx}
%\input myfonts

\newpage
\begin{document}
\begin{questions}

\titledquestion{Basic Background: Big Oh}
Write each of the functions below ($n$ is the positive integer variable) in the Big-Oh notation.

\begin{parts}
\part $O(n^2)$
\part $O(log(n))$
\part $O(1/n)$
\part $O(1)$
\part $O(logn)$
\end{parts}

\titledquestion{Removing Duplicates}[10]
Let $A[1 \dots n]$ be an array of integers. Describe an algorithm that runs in time $O(n \log n)$ and returns an array $B$ whose entries are all the {\em distinct} elements of $A$ (i.e., with no duplicates).


\titledquestion{Proof Practice: Square vs. Multiply}[10]
Suppose I tell you that there is an algorithm that can square any $n$ digit number in time $O(n \log n)$, for all $n\ge 1$. Then, prove that there is an algorithm that can find the product of {\em any two} $n$ digit numbers in time $O(n \log n)$.  [{\em Hint:} think of using the squaring algorithm as a subroutine to find the product.]

\titledquestion{Background: Probability}
Write the answers to the following as functions of $k$:
\begin{parts}
\part[4] Suppose we toss a fair coin $k$ times. What is the probability that we see heads precisely once? 
\part[6] Suppose we have $k$ different boxes, and suppose that every box is colored uniformly at random with one of $k$ colors (independently of the other boxes). What is the probability that all the boxes get distinct colors?
\end{parts}

\titledquestion{Array Sums}[10]
Given an array $A[1 \dots n]$ of integers (not necessarily distinct), find if there exist indices $i, j, k$ such that $A[i] = A[j]+A[k]$.  Can you find an algorithm with running time $o(n^3)$? [NOTE: this is the little-oh notation, i.e., the algorithm should run in time $< cn^3$, for any constant $c$, as $n \rightarrow \infty$.] [{\em Hint:} aim for an algorithm with running time $O(n^2 \log n)$.]

\end{questions}
\end{document}

